Distributed Version Control Systems

### 2010-05-16 paper.tex
Expanded Centralized repository with integration manager

>>>>

In case the number of developers is really big (for instance on an OpenSource project) then a single person cannot deal with the integration from all of them. Then a hierarchycal approach can be taken and there will be a level of integrators who are responsable for merging all the changes from a particular subsystem. A main integrator will merge all the changes from the subsystem's integrator to create and publish the public version.
